Revision Plan for SIGCOMM'24 Paper \#293

### 2024-06-05 revision_plan.tex
update

\noindent\textcolor{red}{\textbf{Proposed modification: }
To address the reviewers' possible misunderstandings regarding the flow scheduling scheme, we will add an analysis under the title of section 4 on page 6 and include additional explanations in the footnotes on page 7.
}
%\noindent\textcolor{blue}{\textbf{Response A.2:}
%Thanks for the reviewer's comments. 
%At the beginning of Section 3, we mentioned that "LCP sends opportunistic packets from the tail end."
%Therefore, HCP and LCP send packets from the beginning and end of the same flow, respectively.
%So, there is no scenario in which there is no HCP flow.
%Since HCP and LCP come from the same flow, they must have the same number and destination.
%}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We will show more details and analysis in Section 2.3 on page 4.
}
%\noindent\textcolor{blue}{\textbf{Response C.1:}
%Thanks for the reviewer’s comments. 
%Indeed, in section 2.3, we mention that \emph{DCTCP marks ECN at the switch for arriving packets if queue occupancy exceeds a threshold K, and the sender cuts the window based on the fraction of ECN marked ACKs. So, when there are multiple concurrent flows, DCTCP may mark ECN for packets from many flows, which may cut windows simultaneously, thus causing a sudden drain on the switch buffer and leaving bandwidth underutilized.}
%To show this point, We run ns-3 simulations with two senders and one receiver sharing the bottleneck. 
%We sample the bottleneck link utilization every 100us for 10ms when DCTCP enters a steady state.
%We plot the results in Figure 1, showing that nearly half of the bandwidth is underutilized.
%}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We will revise it on page 11.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We will add more intuitive reasons in Section 6.2 on page 12.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
Due to time constraints, we will not add further experiment in the paper.
}

>>>>

\noindent\textcolor{red}{\textbf{Proposed modification: }
To address the reviewers' possible misunderstandings regarding the flow scheduling scheme, we have added a summary at the end of section 2 on page 5.
}
%\noindent\textcolor{blue}{\textbf{Response A.2:}
%Thanks for the reviewer's comments. 
%At the beginning of Section 3, we mentioned that "LCP sends opportunistic packets from the tail end."
%Therefore, HCP and LCP send packets from the beginning and end of the same flow, respectively.
%So, there is no scenario in which there is no HCP flow.
%Since HCP and LCP come from the same flow, they must have the same number and destination.
%}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We have shown more details and analysis in Section 2.3 on page 4.
}
%\noindent\textcolor{blue}{\textbf{Response C.1:}
%Thanks for the reviewer’s comments. 
%Indeed, in section 2.3, we mention that \emph{DCTCP marks ECN at the switch for arriving packets if queue occupancy exceeds a threshold K, and the sender cuts the window based on the fraction of ECN marked ACKs. So, when there are multiple concurrent flows, DCTCP may mark ECN for packets from many flows, which may cut windows simultaneously, thus causing a sudden drain on the switch buffer and leaving bandwidth underutilized.}
%To show this point, We run ns-3 simulations with two senders and one receiver sharing the bottleneck. 
%We sample the bottleneck link utilization every 100us for 10ms when DCTCP enters a steady state.
%We plot the results in Figure 1, showing that nearly half of the bandwidth is underutilized.
%}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We have revised it on page 11.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
We have added more intuitive reasons in Section 6.2 on page 12.
}

@@

\noindent\textcolor{red}{\textbf{Proposed modification: }
Due to time constraints, we will address this issue in future work.
}
